### 2016-10-03 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
fix type in Hose acknowledgements

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.

>>>>

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.
